---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fitnessbrowseR

<!-- badges: start -->
<!-- badges: end -->

`fitnessbrowseR` is an R package that provides utilities for retrieving information from the [fitnessb browser](https://fit.genomics.lbl.gov/), a website that compiles data from RB-TnSeq experiments for a variety of microbial hosts and conditions (please, consider reading their [publication](https://mbio.asm.org/content/6/3/e00306-15.full)).

This package is still under development, please report any bug that you find to me at my [email address](viana.guilherme@proton.me), or create a pull request.

Thank you for checking `fitnessbrowseR` out!

## Installation

You can install the development version of fitnessbrowseR with the command below:

``` r
devtools::install_github("viana-guilherme/fitnessbrowseR")
```

## Usage

The package contains three functions at this time
```{r example}
library(fitnessbrowseR)

# prints all organism codes available in the database
getOrganismCodes()

# lists all experimental condition groups for Pseudomonas putida KT2440
getConditions(OrgID = "Putida")

# searches fitness data in all available conditions for genes PP_2675 and PP_2676 in P. putida
searchFitnessBrowser(gene = c("PP_2675", "PP_2676"), OrgID = "Putida")

```
